---
title: "Alcohol vs Seat choice"
author: "Joshua Ramirez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
#Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??
 
 The data came from UCDavis 

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.


$H_A$: The average number drinks is different between at least two rows.   

#Methods
In the data set is a categorical variable, alcohol is numerical

We try to predict alcohol - seat sp we use the Numerical - Categorical helper file

#Results


###Descriptive Results


###Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```

This graph shows..


##Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The numerical summary shows that 

##Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p- value is 0.000006, less than 0.05 so we can reject the null hypotheses
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical summarys 

## Inferential Tests

## Conclusions


